\documentclass[journal,final]{IEEEtran}%,onecolumn
\usepackage[colorlinks,linkcolor=blue,filecolor=blue,citecolor=red,bookmarksnumbered=true]{hyperref}
\usepackage{cite}
\usepackage{graphicx}
\usepackage[cmex10]{amsmath}
\interdisplaylinepenalty=2500
\usepackage{flushend}

\graphicspath{{../reports/}}

\title{Measuring the Global Routing System}

% \author{
% \IEEEauthorblockN{Alexander~Afanasyev}
% \IEEEauthorblockA{Computer Science Department \\
% University of California, Los Angeles \\
% Email: alexander.afanasyev@ucla.edu}
% \and
% \IEEEauthorblockN{Brent~Longstaff}
% \IEEEauthorblockA{Computer Science Department \\
% University of California, Los Angeles \\
% Email: blongstaff@ucla.edu}
% \and
% \IEEEauthorblockN{Neil~Tilley}
% \IEEEauthorblockA{Computer Science Department \\
% University of California, Los Angeles \\
% Email: tilleyns@ucla.edu}%
% }

\author{
Alexander~Afanasyev, %
%,˜\IEEEmembership{Member,˜IEEE,}
Brent Longstaff, and Neil~Tilley \\
\small \{alexander.afanasyev, blongstaff, tilleyns\}@ucla.edu \\ \ \\
\small Computer Science Department \\
\small University of California, Los Angeles
}

\begin{document}

\maketitle

\begin{abstract} % It is so boring that BGP is currently the most important protocol

BGP is currently the most important protocol for insuring the global
connectivity of the Internet. This places a great deal of responsibility on BGP
and creates a number of challenges for it. A primary concern is the impact of
various currently deployed BGP-based techniques on the scalability of the
global routing table. While these techniques provide ISPs with additional
traffic management services (e.g., balancing, multihoming, etc), they have
expanded the routing table size at a pace that exceeds the allocation rate and
is increasing. In our study we present a two-plane analysis of BGP
announcements for the period 2003--2009. First, we correlate globally announced
prefixes with IP allocation data and show how efficiently ISPs announce their
allocated address space. Second, we correlate BGP announcement data to itself
and show various internal factors contributing to the routing table growth.
Finally, we document in which regions of the world routing announcements have
been originating during the period of this study, and we draw conclusions about
the spread of Internet connectivity globally.

% Second, we note occurrences of IP prefix spaces being announced multiple
% times at increasing levels of detail and show these as one of the various
% factors contributing to the routing table growth.

\end{abstract}

\input{01_intro}
\input{03_data}

\input{04_allocations}
\input{05_bgp}

\input{02_related_work}

\input{06_conclusions}

% BGP:
% 128.97.0.0/16, 131.179.0.0/16, 149.142.0.0/16, 164.67.0.0/16, 169.232.0.0/16, 192.35.210.0/24, 192.35.225.0/24, 192.154.2.0/24
%
% ARIN:
% 131.179.0.0/16||direct assignment
% 128.97.0.0/16|AS52|direct assignment
% 192.154.2.0/24|AS52|direct assignment
% 192.35.210.0/24|AS52|direct assignment
% 192.35.225.0/24|AS52|direct assignment
% 149.142.0.0/16|AS52|direct assignment
% 164.67.0.0/16|AS52|direct assignment
% 169.232.0.0/16|AS52|reassigned
%
% 2607:F010:0000:0000:0000:0000:0000:0000/32|AS52|direct allocation

\bibliographystyle{IEEEtranS}
\bibliography{../cs217}
\end{document}
